\documentclass[12pt]{article}

\usepackage{graphicx}
\usepackage[cm]{fullpage}
\usepackage{fixltx2e}
\usepackage{hyperref}
\usepackage{mathtools}
\usepackage{amsmath}
\usepackage{enumerate}
\usepackage{listings}
\usepackage{color}
\usepackage{framed}
\usepackage{eurosym}
\usepackage{changepage}
\setcounter{secnumdepth}{3}
\renewcommand\thesection{\arabic{section}}
\renewcommand\thesubsection{\thesection.\arabic{subsection}}
\definecolor{mygreen}{rgb}{0,0.6,0}
\definecolor{mygray}{rgb}{0.7,0.7,0.7}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\topmargin}{-0.25in}
\setlength{\headheight}{0in}
\setlength{\headsep}{0in}
\setlength{\textwidth}{6.5in}
\setlength{\textheight}{9.25in}
\setlength{\parindent}{7mm}
\setlength{\parskip}{0mm}
\begin{document}
\raggedright{

\input{./titlepage.tex}

\tableofcontents

\newpage

%------------------- Body----------------------%

\section{Objective}
Choose some function \textbf{\texttt{g()}} in R, either built-in to base R or in a CRAN package, to parallelize. Do so in Snow, OpenMP and CUDA (or substitute Thrust for either CUDA or OpenMP but not both), and run timing tests.

\section{Function}
We chose to parallelize the function \texttt{combn()} from the ``combinat" package in CRAN.
\subsection{Description}
Taken from the official documentation:\cite{crandoc}\\
\null
\begin{adjustwidth}{2em}{0pt}
``Generate all combinations of the elements of x taken m at a time. If x is a positive integer, returns
all combinations of the elements of seq(x) taken m at a time. If argument ``fun" is not null, applies
a function given by the argument to each point. If simplify is FALSE, returns a list; else returns a
vector or an array. ``..." are passed unchanged to function given by argument fun, if any.''
\end{adjustwidth}

\subsection{Why Speedups Are Possible}

We have tried \texttt{combn()}, which has the inputs \texttt{combn(x, m, fun=NULL, simplify=TRUE, ...)}, with different inputs for the vector $x$ and value $m$. We noticed that \texttt{combn()} became quite slow once $x$ had a size numbering around 100 or higher and $m$ around 5 or higher, taking several minutes to compute (but not print) its results. We think that we can achieve speedups by dividing the input $x$ equally among the threads/nodes, and parallelizing the work of creating the output matrix or list. The goal is to speed up the function, which, based on its source code, currently computes combinations serially.    

\section{Parallelization}

\input{./openmp.tex}

\input{./snow.tex}

\input{./thrust.tex}

\section{Timing Comparisons}

\input{./timingcomparisons.tex}

\section{Conclusions}


%---------------- End of Body ----------------------%


%---------------- Appendix ----------------------%
\newpage

\appendix

\section{Appendix}

\input{appendix.tex}

\newpage

\addcontentsline{toc}{section}{References}

\begin{thebibliography}{9}
\bibitem{crandoc} 
Scott Chasalow
\textit{Package `combinat'}
\texttt{http://cran.r-project.org/web/packages/combinat/combinat.pdf}

\bibitem{parallelalgorithm} 
Junior Barrera, Alfredo Goldman, and Martha Torres
\textit{A Parallel Algorithm for Enumerating Combinations}
\texttt{http://www.ime.usp.br/~gold/ipp03v3.pdf}
 

\end{thebibliography}


}
\end{document}