\documentclass[12pt]{article}

\usepackage{graphicx}
\usepackage[cm]{fullpage}
\usepackage{fixltx2e}
\usepackage{hyperref}
\usepackage{mathtools}
\usepackage{amsmath}
\usepackage{enumerate}
\usepackage{listings}
\usepackage{color}
\usepackage{framed}
\usepackage{eurosym}
\usepackage{changepage}
\setcounter{secnumdepth}{3}
\renewcommand\thesection{\arabic{section}}
\renewcommand\thesubsection{\thesection.\arabic{subsection}}
\definecolor{mygreen}{rgb}{0,0.6,0}
\definecolor{mygray}{rgb}{0.7,0.7,0.7}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\topmargin}{-0.25in}
\setlength{\headheight}{0in}
\setlength{\headsep}{0in}
\setlength{\textwidth}{6.5in}
\setlength{\textheight}{9.25in}
\setlength{\parindent}{7mm}
\setlength{\parskip}{0mm}
\begin{document}
\raggedright{

\input{./titlepage.tex}

\tableofcontents

\newpage

%------------------- Body----------------------%

\section{Objective}
Choose some function \textbf{\texttt{g()}} in R, either built-in to base R or in a CRAN package, to parallelize. Do so in Snow, OpenMP and CUDA (or substitute Thrust for either CUDA or OpenMP, but not both), and run timing tests.

\section{Function}
We chose to parallelize the function \texttt{combn()} from the ``combinat" package in CRAN.
\subsection{Description}
Taken from the official documentation:\cite{crandoc}\\
\null
\begin{adjustwidth}{2em}{0pt}
``Generate all combinations of the elements of x taken m at a time. If x is a positive integer, returns
all combinations of the elements of seq(x) taken m at a time. If argument ``fun" is not null, applies
a function given by the argument to each point. If simplify is FALSE, returns a list; else returns a
vector or an array. ``..." are passed unchanged to function given by argument fun, if any.''
\end{adjustwidth}

\subsection{Why Speedups Are Possible}

We have tried \texttt{combn()}, which has the inputs \texttt{combn(x, m, fun=NULL, simplify=TRUE, ...)}, with different inputs for the vector $x$ and value $m$. We noticed that \texttt{combn()} became quite slow once $x$ had a size numbering around 100 or higher and $m$ around 5 or higher, taking several minutes to compute (but not print) its results. We think that we can achieve speedups by dividing the input $x$ equally among the threads/nodes, and parallelizing the work of creating the output matrix or list. The goal is to speed up the function, which, based on its source code, currently computes combinations serially.    

\section{Parallelization}

\input{./openmp.tex}

\input{./snow.tex}

\input{./thrust.tex}

\section{Timing Comparisons and Analysis}

\input{./timingcomparisons.tex}

\section{Conclusions}
We expected Thrust to be the fastest out of the three parallel implementations of the \texttt{combn()} function, due to the GPU scheduling large number of threads. However, OpenMP was the fastest because we were able to efficiently divide the workload among the threads. Thrust ended up running slower than our OpenMP implementation, possibly due to Thrust dynamically scheduling the threads in the GPU. Thrust could have run faster if it was further optimized to reduce the amount of overhead by modifying our functor or incorporating other Thrust functions. As for Snow, we expected it to be much faster especially with larger input since the communication overhead would have been hidden by the long calculations. However, Snow ended up performing the poorest, likely because there were also significant parts of the code that were not parallelized (sorting and handling of the output).


%---------------- End of Body ----------------------%


%---------------- Appendix ----------------------%
\newpage

\appendix

\section{Appendix}

\input{appendix.tex}

\newpage

\addcontentsline{toc}{section}{References}

\begin{thebibliography}{9}
\bibitem{crandoc} 
Scott Chasalow
\textit{Package `combinat'}
\texttt{http://cran.r-project.org/web/packages/combinat/combinat.pdf}

\bibitem{parallelalgorithm} 
Junior Barrera, Alfredo Goldman, and Martha Torres
\textit{A Parallel Algorithm for Enumerating Combinations}
\texttt{http://www.ime.usp.br/~gold/ipp03v3.pdf}
 
\bibitem{matlofftutorial} 
Norm Matloff
\textit{Building the Rth routines manually:}
\texttt{http://heather.cs.ucdavis.edu/~matloff/rth.html}

\bibitem{thrustdoc} 
Norm Matloff
\textit{Function Documentation}
\texttt{https://thrust.github.io/doc/group\_\_modifying.html}

\bibitem{gpuandr} 
Norm Matloff
\textit{Parallel Programming with GPUs and R}
\texttt{http://blog.revolutionanalytics.com/2015/01/parallel-programming-
with-gpus-and-r.html}

\bibitem{nextcomb}
\textit{Generating Combinations}
\texttt{https://compprog.wordpress.com/2007/10/17/generating-combinations-1/}


\end{thebibliography}


}
\end{document}